Deep Learning

### 2015-03-27 deepreview.tex
done almost all points of ref 2, now moving to ref 3

Thanks to advances in their architecture~\citep{Hochreiter+Schmidhuber-1997,ElHihi+Bengio-nips8-small} 
and ways of training them~\citep{Sutskever-thesis2012}, recurrent networks 
have been found to be very good at predicting the next character in
text~\citep{Sutskever-et-al-ICML2011} or the next word in a
sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a
time, for example, an English ``encoder'' network can be trained so
that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to) a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen from this
distribution and provided as input to the decoder network it will then
output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.

>>>>

Thanks to advances in their architecture~\citep{Hochreiter+Schmidhuber-1997,ElHihi+Bengio-nips8-small} 
and ways of training them~\citep{Sutskever-thesis2012,Pascanu+al-ICML2013-small}, recurrent networks 
have been found to be very good at predicting the next character in
text~\citep{Sutskever-et-al-ICML2011} or the next word in a
sequence~\citep{Mikolov-et-al-NIPS2013} but they can also be used for
more complex tasks.  After reading an English sentence one word at a
time, for example, an English ``encoder'' network can be trained so
that the final state vector of its hidden units is a good
representation of the thought expressed by the sentence.  This thought
vector can then be used as the initial hidden state of (or as extra
input to) a jointly trained French ``decoder'' network which outputs a
probability distribution for the first word of the French
translation. If a particular first word is chosen from this
distribution and provided as input to the decoder network it will then
output a probability distribution for the second word of the
translation and so on until a full stop is
chosen~\citep{Bahdanau-et-al-arxiv2014,Sutskever-et-al-NIPS2014}.
Overall, this process generates sequences of French words according to
a probability distribution that depends on the English sentence.
